\documentclass[a4paper,11pt]{article}
\pdfoutput=1 

\usepackage{jinstpub} 
\usepackage[utf8]{inputenc}
\usepackage{lineno}

\usepackage[capitalise,noabbrev,nameinlink]{cleveref}
\newlength{\abc}
\settowidth{\abc}{\space}
\AtBeginDocument{%
\renewcommand{\ref}[1]{\mbox{\Cref{#1}}}
\renewcommand{\equationautorefname}{Equation~\hspace{-\abc}}
\renewcommand{\sectionautorefname}{Section\,\negthinspace}
\renewcommand{\subsectionautorefname}{Section\,\negthinspace}
\renewcommand{\subsubsectionautorefname}{Section\,\negthinspace}
\renewcommand{\figureautorefname}{Figure\,\negthinspace}
\renewcommand{\tableautorefname}{Table\,\negthinspace}
}

\input{setup/packages.tex}
\input{setup/commands.tex}

\title{\boldmath Neutron Irradiation and Electrical Characterisation of \\8'' Silicon Pad Sensor Prototypes for the CMS Endcap Calorimeter Upgrade}


\author[a]{Nick Hinton}
\author[b]{Timo Peltola}
\author[c]{Thorben Quast}
\author[c]{Eva Sicking}

\affiliation[a]{Brown University}
\affiliation[b]{Texas Tech University}
\affiliation[c]{CERN Experimental Physics Department}

\collaboration[d]{on behalf of the CMS HGCAL silicon group}

\emailAdd{thorben.quast@cern.ch}

\abstract{
    As part of its HL-LHC upgrade program, the CMS collaboration is planning to replace its existing endcap calorimeters with a highly granular calorimeter (HGCAL). 
    The new calorimeter will be a sampling calorimeter with unprecedented transverse and longitudinal readout for both electromagnetic and hadronic compartments. 
    Due to its compactness, intrinsic time resolution and radiation hardness, silicon has been chosen as active material for the regions exposed to higher radiation. 
    The silicon sensors will be fabricated as \SI{20}{\centi\metre} (8'') wide hexagonal wafers and will be segmented into several hundred sensitive pads which will be read out individually. 
    As part of the sensor qualification strategy, sensor irradiation with neutrons at the Rhode Island Nuclear Science Center followed by electrical tests have been conducted for the first time in 2020/21.
    The completion of this important milestone in the R$\&$D program for this ambitious calorimeter is documented in this work.
    This paper provides detailed account of the associated infrastructural aspects, and explains the procedures followed.
    With it, this work may serve as an instructive inspiration for future R$\&$D on the radiation hardness of large silicon wafers for potential future silicon-based detector concepts.
    Last but not least, the results on the electrical properties of the irradiated HGCAL silicon wafers are presented which may serve as a practical reference for the expected degradation of HGCAL silicon sensors towards the end of its lifetime.
} 
\keywords{Calorimeter, CMS, HGCAL, silicon sensors, neutron irradiation, HL-LHC, electrical properties, leakage, dark current, depletion voltage}

\linenumbers

\begin{document}
\maketitle
\flushbottom

\linenumbers
\input{content/1_introduction.tex}
\input{content/2_sensors.tex}
\input{content/2_irradiation.tex}
\input{content/4_setup.tex}
\input{content/5_results.tex}
\input{content/7_conclusion.tex}
\input{content/acknowledgments.tex}

\appendix
\input{content/appendix/irradiation_rounds.tex}
\input{content/appendix/chuck_temperature.tex}

\bibliographystyle{unsrt}
\bibliography{bib/bib}

\end{document}
